Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex

\lbrack{}Additional cleansing\rbrack{}~We noticed that some of the
tests we found depend on external libraries, which not all selected
engines support. We decided to discard those. For example, many tests
we found were based on Node.js~\cite{node} which\Mar{@Igor, is this
  the reason?  Please, confirm$\rightarrow$} require libraries to be
installed before running the test and different tests require
different sets of libraries. Also, as already mentioned, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.  Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc; we discarded those to avoid repetition and to give
credit where it is due.

\lbrack{}Test Harness\rbrack{}~It is also worth mentioning that some
engines use a custom shell to run tests, including a harness with
specific assertions\Mar{@Igor, can you name which?}. For that, we
needed to make minor changes in the testing infrastructure to be able
to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable functions, which are only available in
certain engines. Since we had to transplant more than 40k test files,
we tried to mock the minimum amount of code possible to make the test
file work in the other engine.\Mar{This seems a different problem
  (tests without assertions). I did not understand how this is related
  to portability?}  For instance, if a test had a statement such as
\texttt{print(1==1);} we manually refactored that statement to
\texttt{assertEquals(1,1)}.  If the change would require more
substantial manual work, we opted to discard the test instead. Overall
we may have manually refactored more than a thousand test files.

@@

For step 2, we considered using the open-source tool
eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
output discrepancy. However, we noticed that eshost-cli does not
handle discrepancies involving crashes. As such, we forked the
eshost-cli GitHub project and implemented that functionality on it. It
is important to note that our checker does not support the case where
the test fails in all engines with a different kind of failure as it
is unclear how to properly relate those failures. Currently, our
infrastructure does not report discrepancy on that case. We left that
as future work as we already found several discrepancies even without
that.

>>>>

\lbrack{}Additional cleansing\rbrack{}~We noticed that some of the
tests we found depend on external libraries, which not all selected
engines support. We decided to discard those. For example, many tests
we found were based on Node.js~\cite{node} which\Mar{@Igor, is this
  the reason?  Please, confirm$\rightarrow$}\Igor{yes, it is. Some Node internal features are 
not included in the JS engine, including some keywords (ie. require, module).
In addiction, a project with nodejs require a package.json with a lot of external dependencies.} require libraries to be
installed before running the test and different tests require
different sets of libraries. Also, as already mentioned, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.  Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc; we discarded those to avoid repetition and to give
credit where it is due.

\lbrack{}Test Harness\rbrack{}~It is also worth mentioning that some
engines uses a custom shell to run tests, including a harness with
specific assertions, \Igor{for example, tests provided by Mozilla contains a lot 
of custom functions (\ie\ assertThrowsInstanceOf, assertEqArray, getPromiseResult).
The shell contains those functions to made the test run correctly.}
\Mar{@Igor, can you name which?}. For that, we
needed to make minor changes in the testing infrastructure to be able
to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable functions, which are only available in
certain engines. Since we had to transplant more than 40k test files,
we tried to mock the minimum amount of code possible to make the test
file work in the other engine.\Mar{This seems a different problem
  (tests without assertions). I did not understand how this is related
  to portability?}\Igor{A test is a simple JS file input.
  Some tests are not well-defined.}  For instance, if a test had a statement such as
\texttt{print(1==1);} we manually refactored that statement to
\texttt{assert(1==1)} which should throw an assertion violation if the condition returns false.
If the change would require more substantial manual work, we opted to discard the test instead. Overall,
we may have manually refactored more than a thousand test files.

@@

For step 2, we considered using the open-source tool
eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
output discrepancy. However, we noticed that eshost-cli does not
handle discrepancies involving crashes. Our tool supports the execution of the
binaries themselves to obtain these fatal errors.
It is important to note that our checker does not support the case where
the test fails in all engines with a different kind of failure as it
is unclear how to properly relate those failures. Currently, our
infrastructure does not report discrepancy on that case. We left that
as future work as we already found several discrepancies even without
that.
